---
title: "Interim results of schemaVR1"
author: "Jörn Alexander Quent"
date: "12 April 2018"
output:
  slidy_presentation: default
  beamer_presentation: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.width = 10, 
                      fig.height= 7, 
                      dpi=300, 
                      out.width="1000px", 
                      out.height="700px")

# Libraries
library(plyr)
library(ggplot2)
library(gridExtra)
library(lmerTest)
library(grid)
library(knitr)

# Functions
pValue <-function(x, sign = '='){
  if (inherits(x, "lm")){
    s <- summary.lm(x)
    x <- pf(s$fstatistic[1L], s$fstatistic[2L], s$fstatistic[3L], lower.tail = FALSE)
    if(x > 1){
      stop("There is no p-value greater than 1")
    } else if(x < 0.001){
      x.converted <- '< .001'
    } else{
      x.converted <- paste(sign,substr(as.character(round(x, 3)), 2,5))
    } 
  } else {
    if(x > 1){
      stop("There is no p-value greater than 1")
    } else if(x < 0.001){
      x.converted <- '< .001'
    } else{
      x.converted <- paste(sign,substr(as.character(round(x, 3)), 2,5))
    } 
  }
  return(x.converted)
}

rValue <-function(x){
  if (inherits(x, "lm")){
    r.squared <- summary(x)$r.squared
    x.converted <- paste('=',substr(as.character(round(r.squared, 3)), 2,5)) 
  } else {
    if (x < 0){
      x.converted <- paste('= -',substr(as.character(abs(round(x, 3))), 2,5), sep = '') 
    } else {
      x.converted <- paste('=',substr(as.character(abs(round(x, 3))), 2,5)) 
    }
  }
  return(x.converted) 
}

# Loading data
load("data/mergedData/exp1Data.RData")

# Adding the normative object/location rating for each target and foil 1 & 2
combData$objLocTargetNorm <- 99
combData$objLocFoil1Norm  <- 99
combData$objLocFoil2Norm  <- 99
for(i in 1:dim(combData)[1]){
  combData$objLocTargetNorm[i] <- combData[i, paste("loc", combData$targetLocation[i], sep = "")]
  combData$objLocFoil1Norm[i]  <- combData[i, paste("loc", combData$foil1Location[i], sep = "")]
  combData$objLocFoil2Norm[i]  <- combData[i, paste("loc", combData$foil2Location[i], sep = "")]
}

# Scaling variables for analysis
combDataScaled                    <- combData
combDataScaled$objLocTargetRating <- scale(combData$objLocTargetRating)
combDataScaled$targetRankPre      <- scale(combData$targetRankPre)
combDataScaled$generalRatingNorm  <- scale(combData$generalRatingNorm)
combDataScaled$generalRatingPost  <- scale(combData$generalRatingPost)
combDataScaled$objLocTargetNorm   <- scale(combDataScaled$objLocTargetNorm)

# Aggregating across all objects
objectAgg <- ddply(combData, c('objNum', 'objName'), summarise, 
                   generalRatingNorm = mean(generalRatingNorm),
                   generalRatingPost = mean(generalRatingPost),
                   afc = mean(accAFC),
                   preRank = mean(targetRankPre),
                   postRating = mean(objLocTargetRating),
                   recall = mean(accRecall, na.rm = TRUE),
                   euclideanDist = mean(euclideanDist))
```

## Desgin

1. Familiarisation in VR 
2. Encoding phase in VR (45 sec) 
3. Practice to pick up objects in VR 
4. Location recall task in VR
5. 3AFC choosing the correct location out of 3
6. Object/location expectancy ratings (3 per times object)
7. General expectancy ratings

## Overall memory performance
```{r}
# Plot: Recall performance
combDataSub1 <- subset(combData, combData$recallNoMemory == 0 | is.na(combData$recallNoMemory))
agg1         <- ddply(combDataSub1, c('subNum'), summarise, accRecall = mean(accRecall, na.rm = TRUE))
p1 <- ggplot(agg1, aes(x = "accRecall" , y = accRecall)) + 
  geom_boxplot(alpha = 0.5, width = 0.5) +
  geom_dotplot(binaxis='y', stackdir='center') +
  labs(y = 'Recall rate', x = ' ', title = 'Recall performance') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(0.9, 1.1)) + 
  theme(plot.margin = margin(10, 10, 10, 10), 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())


# Plot: 3AFC performance
afcCombDataSub <- subset(combData, combData$resCon != 1)
agg2           <- ddply(afcCombDataSub, c('subNum'), summarise, accAFC = mean(accAFC))
p2 <- ggplot(agg2, aes(x = "accAFC" , y = accAFC)) + 
  geom_boxplot(alpha = 0.5, width = 0.5) +
  geom_dotplot(binaxis='y', stackdir='center') + 
  geom_hline(yintercept = 1/3) + 
  annotate('text', x = 0.95, y = (1/3) - 0.03, label = 'Chance (1/3)') + 
  labs(y = 'Accuracy (3AFC)', x = ' ', title = '3AFC performance') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(0.9, 1.1)) + 
  theme(plot.margin = margin(10, 10, 10, 10), 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

grid.arrange(p1, p2, ncol = 2)
```

## Correlation between memory measures
```{r, echo=FALSE}
agg3 <- subset(agg2, subNum < 100)
ggplot(data.frame(accRecall = agg1$accRecall, accAFC = agg3$accAFC), aes(x  = accRecall, y = accAFC)) +
  geom_smooth(method = 'lm') + 
  geom_point() + 
  labs(y = '3AFC accuracy', x = 'Recall rate')
```

## Relationship between expectancy and recall
```{r}
plot1 <- ggplot(objectAgg, aes(x = postRating, y = recall)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (Recall)', x = "Post-ratings expectancy", title = 'Object/location expectancy vs. recall')  + 
  coord_cartesian(ylim = c(0, 1), xlim = c(-100, 100), expand = FALSE)


plot2 <- ggplot(objectAgg, aes(x = preRank, y = recall)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (Recall)', x = "Normative expectancy (ranked)", title = 'Object/location expectancy vs. recall') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 400), expand = FALSE)

plot3 <- ggplot(objectAgg, aes(x = postRating, y = recall)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (Recall)', x = "Post-ratings expectancy", title = 'Object/location expectancy vs. recall') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(-100, 100), expand = FALSE)

plot4 <- ggplot(objectAgg, aes(x = generalRatingNorm, y = recall)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (Recall)', x = "Normative expectancy", title = 'General expectancy vs. recall') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(-100, 100), expand = FALSE)

grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```

## Relationship between expectancy and recall
```{r}
plot5 <- ggplot(objectAgg, aes(x = generalRatingPost, y = recall)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (Recall)', x = "Post-ratings expectancy", title = 'General expectancy vs. recall') + 
  coord_cartesian(ylim = c(0, 1), xlim = c(-100, 100), expand = FALSE)
for (i in 1:dim(objectAgg)[1])  {
  height <- seq(0, 1, length = dim(objectAgg)[1])
plot5 <- plot5 + annotation_custom(
      grob = textGrob(label = paste(as.character(objectAgg$objNum[i]), "=", objectAgg$objName[i]), hjust = 0),
      ymin = height[i],      # Vertical position of the textGrob
      ymax = height[i],
      xmin = 104,         # Note: The grobs are positioned outside the plot area
      xmax = 104)
 }   
plot5 <- ggplot_gtable(ggplot_build(plot5))
plot5$layout$clip[plot5$layout$name == "panel"] <- "off"
grid.arrange(plot5, ncol = 2, nrow = 2)
```

## Recall models
```{r}
subRecall <- subset(combDataScaled, combDataScaled$recallNoMemory == 0)

# Model 1
logiModel <- glmer(accRecall ~  objLocTargetRating + I(objLocTargetRating*objLocTargetRating) + (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
# Model 2
logiModel <- glmer(accRecall ~  targetRankPre + I(targetRankPre*targetRankPre) + (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
# Model 3
logiModel <- glmer(accRecall ~  objLocTargetNorm + I(objLocTargetNorm*objLocTargetNorm) + (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
```

## Recall models
```{r}
# Model 4
logiModel <- glmer(accRecall ~  generalRatingNorm + I(generalRatingNorm*generalRatingNorm)  + (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
# Model 5
logiModel <- glmer(accRecall ~  generalRatingPost + I(generalRatingPost*generalRatingPost)  + (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
```

## Full recall model
```{r}
logiModel <- glmer(accRecall ~  objLocTargetNorm + 
                     I(objLocTargetNorm*objLocTargetNorm) + 
                     objLocTargetRating +
                     I(objLocTargetRating*objLocTargetRating) +
                     generalRatingNorm +
                     I(generalRatingNorm*generalRatingNorm) +
                     targetRankPre +
                     I(targetRankPre*targetRankPre) +
                     generalRatingPost +
                     I(generalRatingPost*generalRatingPost) +
                     answerTime +
                     (1 | subNum), data = subRecall, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
```

## Relationship between expectancy and 3AFC
```{r}
plot1 <- ggplot(objectAgg, aes(x = postRating, y = afc)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (3AFC)', x = "Post-ratings expectancy", title = 'Object/location expectancy vs. 3AFC') + 
  coord_cartesian(ylim = c(0, 1.5), xlim = c(-100, 100), expand = FALSE) #+ 
  #theme(plot.margin = unit(c(1,7,1,1), "lines"))

plot2 <- ggplot(objectAgg, aes(x = preRank, y = afc)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (3AFC)', x = "Normative expectancy (ranked)", title = 'Object/location expectancy vs. 3AFC') + 
  coord_cartesian(ylim = c(0, 1.5), xlim = c(0, 400), expand = FALSE) #+ 
  #theme(plot.margin = unit(c(1,7,1,1), "lines"))

plot3 <- ggplot(objectAgg, aes(x = generalRatingNorm, y = afc)) + 
  geom_point() +
  geom_text(aes(label = objNum),hjust = 0, vjust = 0) + 
  geom_smooth() +  
  labs(y = 'Mean accuracy (3AFC)', x = "Normative expectancy", title = 'General expectancy vs. 3AFC') + 
  coord_cartesian(ylim = c(0, 1.5), xlim = c(-100, 100), expand = FALSE) #+ 
  #theme(plot.margin = unit(c(1,7,1,1), "lines"))
for (i in 1:dim(objectAgg)[1])  {
  height <- seq(0, 1.5, length = dim(objectAgg)[1])
plot3 <- plot3 + annotation_custom(
      grob = textGrob(label = paste(as.character(objectAgg$objNum[i]), "=", objectAgg$objName[i]), hjust = 0),
      ymin = height[i],      # Vertical position of the textGrob
      ymax = height[i],
      xmin = 104,         # Note: The grobs are positioned outside the plot area
      xmax = 104)
 }   

plot3 <- ggplot_gtable(ggplot_build(plot3))
plot3$layout$clip[plot3$layout$name == "panel"] <- "off"

grid.arrange(plot1, plot2, plot3, ncol = 2)
```

## 3AFC models
```{r}
# Model 1
subAFC    <- subset(combDataScaled, combDataScaled$resCon != 1)
logiModel <- glmer(accAFC ~  objLocTargetRating + I(objLocTargetRating*objLocTargetRating) + (1 | subNum), data = subAFC, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)

# Model 2
logiModel <- glmer(accAFC ~  targetRankPre + I(targetRankPre*targetRankPre) + (1 | subNum), data = subAFC, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)

# Model 3
logiModel <- glmer(accAFC ~  generalRatingNorm + I(generalRatingNorm*generalRatingNorm)  + (1 | subNum), data = subAFC, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
```

## Full 3AFC model
```{r}
logiModel <- glmer(accAFC ~  objLocTargetNorm + 
                     I(objLocTargetNorm*objLocTargetNorm) + 
                     objLocTargetRating +
                     I(objLocTargetRating*objLocTargetRating) +
                     generalRatingNorm +
                     I(generalRatingNorm*generalRatingNorm) +
                     targetRankPre +
                     I(targetRankPre*targetRankPre) +
                     generalRatingPost +
                     I(generalRatingPost*generalRatingPost) +
                     answerTime +
                     (1 | subNum), data = subAFC, family = binomial, control = glmerControl(optimizer = "bobyqa"),
                   nAGQ = 1)

kable(summary(logiModel)$coefficients)
```



