---
title: "Analysis of  two line stimulation"
author: "Jörn Alexander Quent"
date: "15 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Libraries
library(ggplot2)
library(MRColour)
library(knitr)
library(reshape2)
library(plyr)

options(scipen = 10)

# Loading data
load('onePoint_sim_results.RData')
onePoint_false_uShapes <- false_uShapes

load('searchLight_sim_results.RData')
searchLight_false_uShapes <- false_uShapes


```

# Distribution of Bayes factors
Note that the BF below are like the analysis that I used order-restricted i.e. $H_0: \beta = 0 \lor H_1: \beta > 0$ or $H_1: \beta < 0$ for the slope low values. 

```{r}
table1 <- data.frame(Method = c('One point', 'One point', 'Search light', 'Search light'),
                     Values = c('Low Values', 'High values', 'Low Values', 'High values'),
                     Maximum = c(max(onePoint_false_uShapes$xlow_OR.BF10), 
                                 max(onePoint_false_uShapes$xhigh_OR.BF10),
                                 max(searchLight_false_uShapes$xlow_OR.BF10),
                                 max(searchLight_false_uShapes$xhigh_OR.BF10)),
                     Median  = c(median(onePoint_false_uShapes$xlow_OR.BF10), 
                                 median(onePoint_false_uShapes$xhigh_OR.BF10),
                                 median(searchLight_false_uShapes$xlow_OR.BF10),
                                 median(searchLight_false_uShapes$xhigh_OR.BF10)))
kable(table1)
```

Above, you can see the raw maximum and median BFs for both methods. The searchlight method does indeed produce higher false BFs.

```{r}
# Create on df
bothMethods <- data.frame(Method = c(rep('One point', dim(onePoint_false_uShapes)[1]),
                                     rep('Search light', dim(searchLight_false_uShapes)[1])),
                          `Low Values` = c(onePoint_false_uShapes$xlow_OR.BF10,
                                           searchLight_false_uShapes$xlow_OR.BF10),
                          `High Values` = c(onePoint_false_uShapes$xhigh_OR.BF10, 
                                           searchLight_false_uShapes$xhigh_OR.BF10))

# Plotting distribution
bothMethods <- melt(bothMethods, id.vars=c("Method"))
bothMethods$value <- log(bothMethods$value)
names(bothMethods) <- c('Method', 'Values', 'log(BF10)')

ggplot(bothMethods, aes(x = Method, y = `log(BF10)`, colour = Values)) +
  geom_hline(yintercept = c(log(3), log(10)), linetype = "dashed") +

  geom_boxplot(outlier.shape = NA, alpha = 0.7) + #avoid plotting outliers twice
  geom_point(position = position_jitterdodge()) +
  labs(title = 'Distribution of Bayes factors with 10000 runs for each method', y = 'log(BF10)') +
  scale_color_mrc() +
  theme(legend.position = c(0, 1),
        legend.justification = c(0, 1)) +
  annotate('text', x = c(0.5, 0.5), y = c(log(3), log(10)) + 0.2, label = c('BF > 3', 'BF > 10')) 
```

This is also evident in the distribution of the log BFs in the figure above. However, as you see only a small number of BFs are actually above 10. Below you see the conditional probabilities that a BF is above 10 given that a U-shape was assumed.

```{r}
# Getting conditional p that BF > 10
onePoint_false_uShapes$low_over10  <- as.numeric(onePoint_false_uShapes$xlow_OR.BF10 > 10)
onePoint_false_uShapes$high_over10 <- as.numeric(onePoint_false_uShapes$xhigh_OR.BF10 > 10)
onePoint_false_uShapes$both_over10 <- as.numeric(onePoint_false_uShapes$xlow_OR.BF10 > 10 &
                                                 onePoint_false_uShapes$xhigh_OR.BF10 > 10)

searchLight_false_uShapes$low_over10  <- as.numeric(searchLight_false_uShapes$xlow_OR.BF10 > 10)
searchLight_false_uShapes$high_over10 <- as.numeric(searchLight_false_uShapes$xhigh_OR.BF10 > 10)
searchLight_false_uShapes$both_over10 <- as.numeric(searchLight_false_uShapes$xlow_OR.BF10 > 10 &
                                                    searchLight_false_uShapes$xhigh_OR.BF10 > 10)
# What the p for getting one or both BF over 10
searchLight_agg <- ddply(searchLight_false_uShapes, 
                         c('br'), 
                         summarise,
                         low_over10 = sum(low_over10),
                         high_over10 = sum(high_over10),
                         both_over10 = sum(both_over10))

table2 <- data.frame(Method = c('One point', 'Search light'),
                     Var1 = c(mean(onePoint_false_uShapes$low_over10 != 0), 
                              mean(searchLight_agg$low_over10 != 0)),
                     var2 = c(mean(onePoint_false_uShapes$high_over10 != 0), 
                              mean(searchLight_agg$high_over10 != 0)),
                     var3 = c(mean(onePoint_false_uShapes$both_over10 != 0), 
                              mean(searchLight_agg$both_over10 != 0)))
names(table2) <- c('Method', 'p(BF_low > 10)', 'p(BF_high > 10)', 'p(BF_both > 10)')
kable(table2)
```

The probability of finding a U-shape (i.e. CI that are not overlapping with 0 for both slopes) is p = `r dim(onePoint_false_uShapes)[1]/10000` for the one point method and p = `r sum(df_agg$uShape != 0)/1000` for the searchlight method. The estimated probability that we get an BF over 10 for the one point method is p = 0, while it is p =`r round((sum(df_agg$uShape != 0)/1000)* mean(searchLight_agg$both_over10 != 0), 4)` for the search light method. Note there are more than 70 points in the plot above for the searchlight because I count only one u-shape per run but for a simulated dataset there were multiple breaking point that showed a u-shape. 

My conclusion is that the searchlight method does introduce a bias but the probability of getting anything but anecdotal evidence per chance is still quite conservative.  
