---
title: "Anonymising data of schemaVR3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Aim of this document

# Library
```{r}
library(assortedRFunctions)
library(plyr)
library(knitr)
```

The package can be downloaded by using:
```{r eval = FALSE}
devtools::install_github("JAQuent/assortedRFunctions")
```
Note that this packages is just a random collection of functions I've written and do not come with any documentation but they are necessary to run the scripts I create. 


# Anonymising data
To able to reproduce the anonymisation, it is important to set a seed. 
```{r}
set.seed(3343)
```

In the next step, I am loading the already preprocessed data that was created with the updateDataset.R script.
```{r}
load("U:/Projects/schemaVR/schemaVR3/ignore_rawData/preprocessed/dataSchemaVR3.RData")
```

The data frame contains all data from all trials from all sub-tasks. In addition to trial, information the data contains information which is unneccesary for analysis but might enable people to identify other participants. This information includes the subject number, date of session, gender and age. For instance, if participants remember their own subject number, they can guess other people's idenity and hence performance. The same is true for the date of the session. All of this can be especially problematic in cases where participants are mostly drawn from a local student population.

## Replacing subject number
In the first step, I therefore anonymise the subject number. For this, I've written a function that can be found anonymise() for my own use. 
```{r}
fileName             <- "U:/Projects/schemaVR/schemaVR3/ignore_rawData/preprocessed/schemaVR3_anonKey"
anonSubNum           <- anonymise(dataSchemaVR3$subNum, fileName = fileName)
dataSchemaVR3$subNum <- anonSubNum
```

The function takes the subject idenitifer in this case running integers and replaces it with alpha numeric strings. 
```{r}
levels(anonSubNum)
```

The function also saves a key as .csv file, with which the data can be de-anonmysed if that is necessary. Obviously, it is very important not to share this information. Therefore, I save it into folder that is not tracked by git. 

# Period of data collection and demographic
The dates and demographic information are only important as summaries for the current analysis. 

```{r}
firstSession  <- as.character(min(dataSchemaVR3$date))
firstSession  <- as.Date(firstSession, '%Y%m%d')

lastSession   <- as.character(max(dataSchemaVR3$date))
lastSession   <- as.Date(lastSession, '%Y%m%d')

testingPeriod <- as.numeric(lastSession - firstSession)

# Delete information from data frame
dataSchemaVR3$date <- NULL
```

All testing was done between `r firstSession` and `r lastSession`, hence the testing period of this experiment was `r testingPeriod` days. 

In the next step, I load the demographic files and bind them to a data frame and calculate the necessary values. For this, one participant is already excluded by altering the file name. 
```{r}
prefix    <- 'demographic_'
location  <- 'U:/Projects/schemaVR/schemaVR3/ignore_rawData/'
allFiles  <- list.files(paste(location, sep = ''))
demoFiles <- allFiles[grep(prefix, allFiles)]
demoPaths <- paste(location, demoFiles, sep = '')

dataSchemaVR3_demo        <- do.call(rbind,lapply(demoPaths, header = FALSE, sep = ' ',read.csv))
names(dataSchemaVR3_demo) <- c('subNum', 'set', 'gender', 'age', 'date', 'startTime', 'endTime')
dataSchemaVR3_demo        <- dataSchemaVR3_demo[order(dataSchemaVR3_demo$subNum), ]

# Deleting information
dataSchemaVR3_demo$subNum <- NULL # To prevent guesses based on age and gender
dataSchemaVR3$age         <- NULL
dataSchemaVR3$gender      <- NULL

# Calculating summary for age
ageMean <- mean(dataSchemaVR3_demo$age)
ageMin  <- min(dataSchemaVR3_demo$age)
ageMax  <- max(dataSchemaVR3_demo$age)
ageSD   <- sd(dataSchemaVR3_demo$age)

# Calculating gender distribution
kable(table(dataSchemaVR3_demo$gender))
```

The age range of the participants (N = `r length(dataSchemaVR3_demo$age)`) was between `r ageMin` and `r ageMax` (Mean = `r round(ageMean, 2)`, SD = `r round(ageSD, 2)`). 

# Saving data
```{r}
save.image('dataSchemaVR3.RData')
```