---
title: "Power analysis for schemaVR2"
author: "Jörn Alexander Quent"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 6
    theme: united
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(eval.after = 'fig.cap')
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.width = 10, 
                      fig.height= 7, 
                      dpi=300, 
                      out.width="1200px", 
                      out.height="700px")
options(scipen = 30)
```

# Introduction
This script calculates the needed sample size for schemaVR2 to detect a quadratic effect with an estimate of 0.51 and SE of 0.22. This is based on model 7 for schemaVR1. This model was choosen because it shows the lowest effect from all models that show this effect for schemaVR1. The power analysis was run with R package SIMR from @Green2016.

# Preliminary stuff
## Libraries
```{r}
library(lmerTest)
library(knitr)
library(simr)
```

## Data
```{r}
# Loading data
#load("exp1Data.RData")


# Adding the normative object/location rating for each target and foil 1 & 2
combData$objLocTargetNorm <- NA
combData$objLocFoil1Norm  <- NA
combData$objLocFoil2Norm  <- NA
for(i in 1:dim(combData)[1]){
  combData$objLocTargetNorm[i] <- combData[i, paste("loc", combData$targetLocation[i], sep = "")]
  combData$objLocFoil1Norm[i]  <- combData[i, paste("loc", combData$foil1Location[i], sep = "")]
  combData$objLocFoil2Norm[i]  <- combData[i, paste("loc", combData$foil2Location[i], sep = "")]
}
```

## Functions
```{r}
sigStars <- function(x){
  # Adding stars to indicate significance
  stars <- rep("", length(x))
  stars[x <= 0.1   & x > 0.05]   <- '.' # trend
  stars[x <= 0.05  & x > 0.01]   <- '*'
  stars[x <= 0.01  & x > 0.001]  <- '**'
  stars[x <= 0.001]              <- '***'
  return(stars)
}

createResultTable <- function(x){
  # Creating a nice looking table
  if(inherits(x, "glmerMod")){
    # For glmer table
    xTable        <- summary(x)$coefficients
    xTable        <- data.frame(xTable)
    xTable[, 1]   <- round(xTable[, 1], 2)
    xTable[, 2]   <- round(xTable[, 2], 2)
    xTable[, 3]   <- round(xTable[, 3], 2)
    xTable[, 4]   <- round(xTable[, 4], 4)
    xTable        <- cbind(xTable, sigStars(xTable[, 4]))
    names(xTable) <- c('Estimate', 'SE', 'Z', 'P', 'Sig')
  } else if(inherits(x, 'merModLmerTest')){
    xTable        <- summary(x)$coefficients
    xTable        <- data.frame(xTable)
    xTable[, 1]   <- round(xTable[, 1], 2)
    xTable[, 2]   <- round(xTable[, 2], 2)
    xTable[, 3]   <- round(xTable[, 3], 2)
    xTable[, 4]   <- round(xTable[, 4], 2)
    xTable[, 5]   <- round(xTable[, 5], 4)
    xTable        <- cbind(xTable, sigStars(xTable[, 5]))
    names(xTable) <- c('Estimate', 'SE', 'DF', 'T', 'P', 'Sig')
  } else if(inherits(x, 'anova')){
    if(attributes(x)$heading == "Analysis of Variance Table of type III  with  Satterthwaite \napproximation for degrees of freedom"){
      # Only ANOVA on lmerTest models with Satterthwaite approximation
      xTable        <- data.frame(x)
      xTable[, 1]   <- round(xTable[, 1], 2)
      xTable[, 2]   <- round(xTable[, 2], 2)
      xTable[, 3]   <- round(xTable[, 3], 2)
      xTable[, 4]   <- round(xTable[, 4], 2)
      xTable[, 5]   <- round(xTable[, 5], 2)
      xTable[, 6]   <- round(xTable[, 6], 4)
      xTable        <- cbind(xTable, sigStars(xTable[, 6]))
      names(xTable) <- c('SS', 'MSS', 'nDF', 'dDF', 'F', 'P', 'Sig') 
    } else {
      xTable <- data.frame('######', 'No known model', '######')
      names(xTable) <- c('%%%', '***', '&&&')
    }
  } else {
    xTable <- data.frame('######', 'No known model', '######')
    names(xTable) <- c('%%%', '***', '&&&')
  }
  return(xTable)
}
```

# Model 7 from schemaVR1
```{r}
combDataScaled                    <- combData
combDataScaled$generalRatingNorm  <- scale(combData$generalRatingNorm)
combDataScaled$objLocTargetNorm   <- scale(combDataScaled$objLocTargetNorm)

model7 <- glmer(accAFC ~  objLocTargetNorm + 
                  I(objLocTargetNorm*objLocTargetNorm) + 
                  generalRatingNorm +
                  (1 | subNum), data = combDataScaled, 
                family = binomial, 
                control = glmerControl(optimizer = "bobyqa"),
                nAGQ = 1)

kable(createResultTable(model7))
```

Retrospective 'observed power' for quadratic term in model 7:
```{r}
powerSim(model7, 
         test = fixed("I(objLocTargetNorm * objLocTargetNorm)", method = 'z'), 
         progress = FALSE)
```

# Power curve
```{r}
# Number of runs in monte-carlo simulation
simrOptions(nsim = 1000)

# Extent model to 25 participants to plot power curve
model7 <- extend(model7,
                 along = 'subNum',
                 n = 25)

pc1 <- powerCurve(model7, 
                  test = fixed("I(objLocTargetNorm * objLocTargetNorm)", method = 'z'),
                  along = "subNum", 
                  progress = FALSE)
print(pc1)
plot(pc1)
```

We choose the number of participants where the power is 80%. 

# References