---
title: "Re-assessing correlation between R/K and expectancy"
author: "Jörn Alexander Quent"
date: "21 September 2018"
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '6'
  word_document:
    toc: yes
    toc_depth: '6'
fontsize: 12pt
geometry: left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm
---

```{r setup, include=FALSE}
options(scipen = 30)

# Libraries
library(plyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(grid)

# Settings
opts_chunk$set(echo = TRUE,
               warning = FALSE,
               message = FALSE,
               eval = TRUE,                     
               fig.width = 10, 
               fig.height = 7, 
               dpi = 300)
opts_knit$set(eval.after = 'fig.cap')
```

# Aim
Before I start the next experiment, I want to make sure that the spread of the objects is actually good. Even though they were selected to be good (see [here](https://jaquent.github.io/2018/0917_schemaVR3_stimulusSelection.html)), I just want to be on the save side. 

# Preparation
```{r}
load("schemaVR3_selectionData_20180823_1852.RData")
```

# Visualising spread of objects
```{r}
sets       <- c(848, 498, 388, 246, 111)

getMeanRanks <- function(meanRankedRatings, sortedtargets, x){
  return(meanRankedRatings[cbind(seq_along(sortedtargets[, x]),  sortedtargets[, x])])
}

Expectancy <- as.vector(sapply(sets, function(x)
  getMeanRanks(meanRankedRatings, sortedtargets, x = x)), mode = "double")

kitchen <- c(rep('kitchen', 12), rep('non-kitchen', 8))

setSpreads <- data.frame(Set = as.factor(rep(sets, each = 20)),
                         Kitchen = rep(kitchen, 5),
                         Expectancy = Expectancy)

ggplot(setSpreads, aes(x = Set, 
                       y =Expectancy, 
                       colour = Kitchen)) +
  geom_jitter(height = 0, width = 0.05) +
  coord_cartesian(xlim = c(0.8, 5.2), ylim = c(1, 400), expand = FALSE)
```

As can be seen above the spread of the kitchen objects is really good. In contrast the non-kitchen objects cluster in middle, which however is not surprising if one assumes that objects that are not really expected to be found in a kitchen also do not have an expected location. Therefore, it will be important to covary out general expectancy in the models of schemaVR3.  